Policy optimization for dynamic spatiotemporal systems \hspace{1em} \insertframenumber

### 2014-08-07 pot/LaTeX/jsm2014.tex
Draft updates for JSM

\begin{frame}{Predicted 95th quantile}
\centering
\begin{figure}
    \includegraphics[width=.5\linewidth]{./plots/quantile-95-gau.pdf}
    \includegraphics[width=.5\linewidth]{./plots/quantile-95-t19.pdf}
    \caption{Predicted 95th quantile using Gaussian and $t$ thresholded at $T=0.9$}
\end{figure}
\end{frame}

\begin{frame}{Predicted 99th quantile}
\centering
\begin{figure}
    \includegraphics[width=.5\linewidth]{./plots/quantile-99-gau.pdf}
    \includegraphics[width=.5\linewidth]{./plots/quantile-99-t19.pdf}
    \caption{Predicted 95th quantile using Gaussian and $t$ thresholded at $T=0.9$}
\end{figure}
\end{frame}

\begin{frame}{Probability of exceedance}
\centering
\begin{figure}
    \includegraphics[width=.5\linewidth]{./plots/p-exceed-std-gau.pdf}
    \includegraphics[width=.5\linewidth]{./plots/p-exceed-std-t19.pdf}
    \caption{Probability of exceeding the 75 ppb ozone standard using Gaussian and $t$ thresholded at $T=0.9$}
\end{figure}
\end{frame}

\begin{frame}{Simulation study}
  \begin{itemize} \setlength{\itemsep}{0.5em}
    \item 6 different data settings:
    \begin{itemize}
    	\item Gaussian vs $t$ vs skew-$t$ marginal distribution
        \item $K=1$ partition vs $K=5$ partitions
    \end{itemize}
    \item Preliminary results suggest that there may be a modest improvement in quantile scores from thresholding when the data come from a $t$ distribution with $K=5$ partitions.
  \end{itemize}
\end{frame}

@@

\begin{frame}{Questions}
  \begin{itemize} \setlength{\itemsep}{0.5em}
    \item Questions?
    \item Thank you for your attention.
    \item Acknowledgment: This work was funded by EPA STAR award R835228.
  \end{itemize}
\end{frame}

>>>>

\begin{frame}{Predicted 95th quantile}
\centering
\begin{figure}
    \includegraphics[width=.5\linewidth]{./plots/quantile-95-gau.pdf}
    \includegraphics[width=.5\linewidth]{./plots/quantile-95-t10.pdf}
    \caption{Predicted 95th quantile using Gaussian and $t$}
\end{figure}
\end{frame}

\begin{frame}{Predicted 95th quantile}
\centering
\begin{figure}
    \includegraphics[width=.5\linewidth]{./plots/quantile-95-t10.pdf}
    \includegraphics[width=.5\linewidth]{./plots/quantile-95-t19.pdf}
    \caption{Predicted 95th quantile using $t$ and $t$ thresholded at $T=0.9$}
\end{figure}
\end{frame}

\begin{frame}{Predicted 99th quantile}
\centering
\begin{figure}
    \includegraphics[width=.5\linewidth]{./plots/quantile-99-gau.pdf}
    \includegraphics[width=.5\linewidth]{./plots/quantile-99-t10.pdf}
    \caption{Predicted 99th quantile using Gaussian and $t$}
\end{figure}
\end{frame}

\begin{frame}{Predicted 99th quantile}
\centering
\begin{figure}
    \includegraphics[width=.5\linewidth]{./plots/quantile-99-t10.pdf}
    \includegraphics[width=.5\linewidth]{./plots/quantile-99-t19.pdf}
    \caption{Predicted 99th quantile using $t$ and $t$ thresholded at $T=0.9$}
\end{figure}
\end{frame}

\begin{frame}{Probability of exceedance}
\centering
\begin{figure}
    \includegraphics[width=.5\linewidth]{./plots/p-exceed-std-gau.pdf}
    \includegraphics[width=.5\linewidth]{./plots/p-exceed-std-t10.pdf}
    \caption{Probability of exceeding the 75 ppb ozone standard using Gaussian and $t$}
\end{figure}
\end{frame}

\begin{frame}{Probability of exceedance}
\centering
\begin{figure}
    \includegraphics[width=.5\linewidth]{./plots/p-exceed-std-t10.pdf}
    \includegraphics[width=.5\linewidth]{./plots/p-exceed-std-t19.pdf}
    \caption{Probability of exceeding the 75 ppb ozone standard using $t$ and $t$ thresholded at $T=0.9$}
\end{figure}
\end{frame}

\begin{frame}{Simulation study}
  \begin{itemize} \setlength{\itemsep}{0.5em}
    \item 6 different data settings:
    \begin{itemize}
    	\item Gaussian vs $t$ vs skew-$t$ marginal distribution
        \item $K=1$ partition vs $K=5$ partitions
    \end{itemize}
    \item Preliminary results are inconclusive.
  \end{itemize}
\end{frame}

@@

\begin{frame}{Questions}
  \begin{itemize} \setlength{\itemsep}{0.5em}
    \item Questions?
    \item Thank you for your attention.
    \item Acknowledgment: This work was funded by EPA STAR award R835228
  \end{itemize}
\end{frame}
